### 2015-05-08 fundamentals/impl.tex
reviewer 2:page 23: typing error: and it cannot... but is cannot -> but it cannot
reviewer 2: page 20: What is BatchReactor?

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & BatchReactor & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. \\
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Facility & Fab$^*$ & This facility fabricates fuel material based on separated streams. \\
Facility & Reactor$^*$ & This facility, based on BatchReactor, requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
Facility & Separations$^*$ & This facility separates an incoming material into specified streams. \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple
simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
1.3 are marked with $^*$.}
\label{tab:cycamore}
\end{table}

@@

Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software
development components that comprise the \Cyclus verification strategy.
Each of these on its own is a valuable addition to \gls{QA} but is cannot be the
entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly
adhered to, they present a fortress to protect against poorly designed or otherwise undesirable code.

>>>>

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & BatchReactor$^{**}$ & A reactor model that handles batch refueling, based on pre-determined recipes of compositions.\\
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Facility & Fab$^*$ & This facility fabricates fuel material based on separated streams. \\
Facility & Reactor$^*$ & This facility has capabilities of BatchReactor (above), and requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
Facility & Separations$^*$ & This facility separates an incoming material into specified streams. \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple
simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
1.3 are marked with $^*$. Facilities deprecated in version 1.3 are marked with 
$^{**}$.}
\label{tab:cycamore}
\end{table}

@@

Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software
development components that comprise the \Cyclus verification strategy.
Each of these on its own is a valuable addition to \gls{QA} but it cannot be the
entire answer to the requirements imposed by \gls{NQA1}. Taken together and strictly
adhered to, they present a fortress to protect against poorly designed or otherwise undesirable code.
